\documentclass[11pt,a4paper,sans]{moderncv}  
  
% ModernCV themes  
\moderncvstyle{casual}   
\moderncvcolor{blue}                                 
  
% Character encoding  
\usepackage{fontspec}  
  
% Adjust the page margins  
\usepackage[scale=0.75, top=2cm, bottom=2cm]{geometry}  
  
% Personal Data  
\firstname{Brandon}  
\lastname{Beck}  
\title{Technical Operator \& AI Practitioner}                                 
\address{1821 Fuller}{Winfield, KS 67156}   
\phone[mobile]{620.222.6688}  
\email{beckb0608@gmail.com}  
\homepage{becksbrainstorms.com}
  
%----------------------------------------------------------------------------------  
%            content  
%----------------------------------------------------------------------------------  
\begin{document}  
\makecvtitle  
  
\section{Professional Summary}  
Adaptable and detail-oriented professional with 19 years of diverse experience spanning technical contracting, precision manufacturing, retail operations, and high-stakes healthcare. Proven track record of mastering complex systems, from AI logic evaluation and Android app development to CNC machine operation and strict medical compliance. Possesses a continuous builder's mindset with a strong foundation in technical troubleshooting, quality assurance, and autonomous project management.
  
\section{Education \& Continuous Development}  
\cventry{2024}{Google AI Essentials Specialization}{Coursera / Google}{Online}{}{Mastered the 5-step prompting framework, ethical AI integration, and multimodal problem-solving.}  
\cventry{2024}{Technical Development Curriculums}{Independent Study}{Online}{}{Completed a comprehensive 30-day Python programming curriculum, Android Studio app development frameworks, and Home Assistant integrations.}
\cventry{2006}{High School Diploma}{Winfield High School}{Winfield, KS}{}{}  
  
\section{Technical \& Independent Projects}  
\cventry{2024--Present}{Lead Developer}{Spark Delivery Insights Tool}{Independent Project}{}{  
\begin{itemize}  
    \item Developed a custom AI-driven tracking tool to categorize and analyze delivery performance data.  
    \item Implemented Google’s prompting framework to automate data extraction from unstructured logs.  
    \item Utilized Chain-of-Thought reasoning to calculate complex net-earning variables and efficiency metrics.  
    \item Practiced iterative refinement to ensure high-accuracy outputs for personal financial tracking.  
\end{itemize}}  

\cventry{2025--Present}{App Developer}{Custom OBD-II Android Application}{Independent Project}{}{  
\begin{itemize}  
    \item Designed and deployed a custom mobile application utilizing Bluetooth integration to read real-time diagnostic OBD-II data.  
    \item Implemented data logging and asynchronous background tasks using Python and Android Studio frameworks.  
\end{itemize}}  
  
\section{Professional Experience}  
\cventry{2024--Present}{Independent Technical Contractor}{DataAnnotation.tech \& Walmart Spark}{Winfield, KS}{}{
\begin{itemize}
    \item Evaluate and train advanced AI models through complex prompt engineering, rigorous logic testing, and code evaluation (including Python scripts).
    \item Manage independent workflows, logistics routing, and platform analytics to maximize operational efficiency.
\end{itemize}}

\cventry{2025--Present}{Precision Machine Operator (Conformal Coating / Selective Solder)}{S\&Y Industries}{Winfield, KS}{}{  
\begin{itemize}  
    \item Operate and maintain complex manufacturing machinery (CNC Selective Solder and Conformal Coating) with zero-defect targets.  
    \item Utilize AI-assisted research and logic troubleshooting to interpret schematics, analyze operational deviations, and minimize machine downtime.  
    \item Maintain strict adherence to IPC quality standards and organizational data privacy protocols.  
\end{itemize}}  
  
\cventry{2017--2024}{Retail Sales \& Logistics Associate}{Walmart}{Winfield, KS}{}{  
\begin{itemize}  
    \item \textbf{Overnight Stocking (2021--2024):} Managed high-volume inventory replenishment, streamlined warehouse workflows, and met precise daily productivity metrics.  
    \item \textbf{Sporting Goods (2020--2021):} Handled specialized sales, precision inventory tracking, and regulatory compliance.  
    \item \textbf{Lawn \& Garden (2018--2020):} Managed seasonal transitions, complex outdoor inventory control, and customer consultations.  
    \item \textbf{Cashier (2017--2018):} Facilitated high-accuracy point-of-sale transactions and cross-functional team communication.  
\end{itemize}}  
  
\cventry{2014--2017}{Solderer / Coating Operator}{S\&Y Industries}{Winfield, KS}{}{  
\begin{itemize}  
    \item Specialized in wave soldering, selective soldering, and conformal coating for intricate, high-density electronic assemblies.  
    \item Performed precision hand-soldering and strict quality control inspections on circuit board components.  
\end{itemize}}  
  
\cventry{2006--2015}{Certified Medication Aide (CMA) / Certified Nursing Assistant (CNA)}{Kansas Veterans Home (KVH)}{Winfield, KS}{}{  
\begin{itemize}  
    \item Delivered high-level patient care and executed precise medication administration in a fast-paced, high-stakes environment.  
    \item Maintained 100\% accuracy in medication dosing and meticulous medical documentation over a stable, multi-year tenure.  
    \item Demonstrated exceptional crisis management skills and total adherence to state, federal, and HIPAA privacy standards.  
\end{itemize}}  
  
\section{Skills \& Core Competencies}  
\cvitem{AI \& Technical}{Prompt Engineering (Google Framework), Chain-of-Thought Logic, Python, Android Studio, Code Evaluation, Home Assistant Integration}  
\cvitem{Operations \& CNC}{Selective Soldering, Conformal Coating, Wave Soldering, CNC Machine Calibration, IPC Standards, Schematics}  
\cvitem{Compliance \& QA}{Meticulous Documentation, HIPAA Standards, Medical Administration, Regulatory Compliance, Inventory Control}  
\cvitem{Core Strengths}{Long-term Reliability, Technical Troubleshooting, Autonomous Project Management, System Diagnostics}  
  
\end{document}
